What's in a name? On the automated topic naming of software maintenance activities

### 2010-03-06 icpc/icpc2010.tex
spell checked

\caption{Maxdb Mulan results per Mulan learner}

@@

\begin{comment}
           exp2 exp3 learn  B 2nd
maxdb port 0.55 0.66 0.74   L 3
maxdb eff  0.55 0.64 0.67   L 3
maxdb rel  0.76 0.65 0.73   2 2
maxdb fun  0.52 0.66 0.81   L 3
maxdb main 0.52 0.56 0.78   L 3
maxdb use  0.62 0.59 0.75   L 2

>>>>

\caption{MaxDB Mulan results per Mulan learner}

@@

\begin{comment}
           exp2 exp3 learn  B 2nd
MaxDB port 0.55 0.66 0.74   L 3
MaxDB eff  0.55 0.64 0.67   L 3
MaxDB rel  0.76 0.65 0.73   2 2
MaxDB fun  0.52 0.66 0.81   L 3
MaxDB main 0.52 0.56 0.78   L 3
MaxDB use  0.62 0.59 0.75   L 2
